env_and_copies_stats

### 2023-04-11 code/analysis_code/stats/3_correlation.qmd
swirtched corr plots to spearmans

@@

```{r}
#Blind Oso
bo<-
  bo %>%
  mutate(amm = log10(amm), #Log-transforms data
         din_dip = log10(din_dip),
         doc = log10(doc),
         dust = log10(dust)) %>%
  select(!c(secchi, tn, tdn, don)) #Removes non-parametric data

#Canals
c2<- 
  c2 %>%
  mutate(orthop = log10(orthop),
         dust = log10(dust)) %>%
  select(!c(secchi, nn, sil, doc,toc, tn))

#Gulf
rd<- 
  rd %>%
  mutate(doc = log10(doc),
         toc = log10(toc),
         dust = log10(dust)) %>%
  select(!c(sal, do_mgl, secchi, nn, tn))
```

@@

```{r, include = FALSE}
b<- cor(bo) #Default method = pearson
round(b,2) #Round correlation coeff to "x" digits

c<- cor(c2)
round(c,2)

r<- cor(rd)
round(r,2)
```

@@

```{r}
corrplot(b, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45,
         title = "Blind Oso",  mar=c(0,0,1,0)) #Adds and lowers title

corrplot(c, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45,
         title = "Canals", mar=c(0,0,1,0))

corrplot(r, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45,
         title = "Gulf", mar=c(0,0,1,0))
```

@@

```{r}
# Insignificant correlation are crossed
#corrplot(bclean$r, type="upper", order="hclust", 
        # p.mat = bclean$P, sig.level = 0.01, insig = "blank")
# Insignificant correlations are leaved blank
#corrplot(bclean$r, type="upper", order="hclust", 
        # p.mat = bclean$P, sig.level = 0.01, insig = "blank")
```

>>>>

<!--# If we are using a nonparametric correlation (i.e. Spearman) we do not log-transform data -->

@@

```{r}
#Blind Oso
#bo<-
  #bo %>%
 # mutate(amm = log10(amm), #Log-transforms data
        # din_dip = log10(din_dip),
        # doc = log10(doc),
        # dust = log10(dust),
         #chl = log10(chl)) %>%
 # select(!c(secchi, tn, tdn, don)) #Removes non-parametric data

#Canals
#c2<- 
  #c2 %>%
  #mutate(orthop = log10(orthop),
         #dust = log10(dust)) %>%
  #select(!c(secchi, nn, sil, doc,toc, tn))

#Gulf
#rd<- 
 # rd %>%
 # mutate(doc = log10(doc),
      #   toc = log10(toc),
        # dust = log10(dust)) %>%
  #select(!c(sal, do_mgl, secchi, nn, tn))
```

@@

```{r, include = FALSE}
b<- cor(bo, method = "spearman") #Default method = pearson
round(b,2) #Round correlation coeff to "x" digits

c<- cor(c2, method = "spearman")
round(c,2)

r<- cor(rd, method = "spearman")
round(r,2)
```

@@

<!--# This is using Spearman's with raw data -->

```{r}
corrplot(b, type = "upper", 
         tl.col = "black", tl.srt = 45,
         title = "Blind Oso",  mar=c(0,0,1,0)) #Adds and lowers title

corrplot(c, type = "upper", 
         tl.col = "black", tl.srt = 45,
         title = "Canals", mar=c(0,0,1,0))

corrplot(r, type = "upper", 
         tl.col = "black", tl.srt = 45, mar=c(0,0,1,0))
         title(main = "Gulf" )
```

@@

```{r}
# Insignificant correlation are crossed
#corrplot(bclean$r, type="upper", order="hclust", 
        # p.mat = bclean$P, sig.level = 0.05, insig = "blank")

#corrplot(cclean$r, type="upper", order="hclust", 
        # p.mat = cclean$P, sig.level = 0.05, insig = "blank")

#corrplot(rclean$r, type="upper", order="hclust", 
         #p.mat = rclean$P, sig.level = 0.05, insig = "blank")

### 2023-04-11 code/analysis_code/stats/4_uni_variate.qmd
swirtched corr plots to spearmans

```{r}
dust<- dust0 %>%
  filter(!is.na(date),
         date %in% as.Date("2022-07-04"):as.Date("2022-07-19")) %>%
  mutate(t7sum = log10(t7sum)) #Log transform Dust conc (as it is not normal)

@@

```{r}
master0<- 
  dust %>% full_join(data) %>%
  filter(hr_cst %in% "01") #While this is technically not for hour 1, this gets ride of all duplicates for the sake of analysis.
master<- master0[c(1,8,14,32)] #Select columns of interest

@@

```{r}
fig1<- bo2 %>% ggplot(aes(x = lag, y = copies_mL)) +
  geom_point() +
  stat_smooth(method = "lm")+
  stat_correlation(method = "pearson")+
  labs(title = "LM DustxCopies (BO+1)",
       x = "log(dust)")

fig2<- c22 %>% ggplot(aes(x = lag, y = copies_mL)) +
  geom_point() +
  stat_smooth(method = "lm")+
  stat_correlation(method = "pearson")+
  labs(title = "LM DustxCopies (C2+2)",
       x = "log(dust)")

fig3<- rd2 %>% ggplot(aes(lag, copies_mL)) +
  geom_point() +
  stat_smooth(method = "lm")+
  stat_correlation(method = "pearson")+
  labs(title = "LM DustxCopies (RD+1)",
       x = "log(dust)")
```

>>>>

```{r}
dust<- dust0 %>%
  filter(!is.na(date),
         date %in% as.Date("2022-07-04"):as.Date("2022-07-19")) #%>%
  #mutate(t7sum = log10(t7sum)) #Log transform Dust conc (as it is not normal)

@@

```{r}
master0<- 
  dust %>% full_join(data) %>%
  filter(hr_cst %in% "01") #While this is technically not for hour 1, this gets ride of all duplicates for the sake of analysis.
master<- master0[c(1,8,14,34)] #Select columns of interest

@@

```{r}
bo2 %>% ggplot(aes(x = lag, y = copies_mL)) +
  geom_point() +
  stat_smooth(method = "lm")+
  stat_correlation(method = "spearman")+
  labs(title = "LM DustxCopies (BO+1)",
       x = "log(dust)")
 c22 %>% ggplot(aes(x = lag, y = copies_mL)) +
  geom_point() +
  stat_smooth(method = "lm")+
  stat_correlation(method = "spearman")+
  labs(title = "LM DustxCopies (C2+2)",
       x = "log(dust)")
 rd2 %>% ggplot(aes(lag, copies_mL)) +
  geom_point() +
  stat_smooth(method = "lm")+
  stat_correlation(method = "spearman")+
  labs(title = "LM DustxCopies (RD+1)",
       x = "log(dust)")
